Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (uniform distribution)

### 2022-06-24 Manual.Rmd
Updated manual with diagram and title

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for Poisson Regression (Uniform Distribution)"
output: github_document
---

@@

* The project ***"Uniform_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Uniform"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the Poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.

@@

* Based on the real model of the Poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Uniform_Special.R***.

@@

* As of now the model parameters and their respective response compositions are 
1. $\theta=[-1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
2. $\theta=[-1.0, 0.5, 0.5, 0.7]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
3. $\theta=[-1.0, 0.5, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
4. $\theta=[-1.0, 0.5, 0.5, 0.5, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.

* For each model structure covariate data was generated only through a Uniform distribution.

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (uniform distribution)"
output: github_document
---

@@

* The project ***"Uniform_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Uniform"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.

@@

* Based on the real model of the poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Uniform_Special.R***.

@@

* As of now the model parameters and their respective response compositions are 
1. $\theta=[1.0, 0.3, 0.3]$ generates data for Model 1 of $x_1,x_2$.
2. $\theta=[1.0, 0.7,-0.5, 0.4]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
3. $\theta=[1.0,-0.4, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
4. $\theta=[1.0, 0.5, 0.5,-0.3, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.

* For each model structure covariate data was generated only through a uniform distribution.
